\bf Supplementary Material: What is the Best Way to Display Two Time Series to Read Association?

### 2016-02-01 paper/paper.Rnw
Restructure

<<setup, echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
library(ggplot2)
library(mnormt)
library(tidyr)
library(knitr)
library(nullabor)
library(dplyr)
library(mFilter)
library(grid)
library(gridExtra)
library(stringr)
#library(readr)
#library(lubridate)
# Convert these to read_csv at some point
correl <- read.csv("correlations.csv", stringsAsFactors = FALSE) ##Correlations of every plot in every lineup
full <- read.csv("full.csv", row.names=1, stringsAsFactors = FALSE) ##MTurk evaluations
prediction <- read.csv("sas/predfit.csv") ##fitted data from SAS
time.fit <- read.csv("sas/time.csv") ##coefficients for time model from SAS
powercoef <- read.csv("sas/PowerEstimates.csv") ##coefficients for power model from SAS

@@

\begin{figure}[htbp]
  \centering
    \begin{subfigure}[htbp]{0.45\textwidth}
    <<nzd, error=FALSE, message=FALSE, warning=FALSE, echo=FALSE>>=
    library(dplyr)
    library(tidyr)
    library(ggplot2)
    rates <- select(read.csv("rates.csv"), date, AUD, CNY, NZD)[36:69,]
    rates <- mutate(rates, AUD2=(AUD-mean(AUD))/sd(AUD), CNY2=(CNY-mean(CNY))/sd(CNY)) #scaling
    ggplot(data=rates, aes(x=AUD, y=NZD)) + geom_point()
    @
    \end{subfigure}
    \begin{subfigure}[htbp]{0.45\textwidth}
    <<nzd2, dependson='nzd', error=FALSE, message=FALSE, warning=FALSE, echo=FALSE>>=
    rates_l <- gather(rates, currency, value, -date)
    ggplot(data=subset(rates_l, currency != "CNY" & currency != "CNY2" & currency != "AUD2"), aes(x=as.Date(date), y=value, colour=currency)) + geom_line()
    @
    \end{subfigure}
  \caption{Cross-rates for Australian and NZ dollars against US dollar, from Mar 30-May 2, 2015, shown using a scatterplot (left) and overlaid line graph (right). From which plot is correlation more accurately read? Point-wise correlation between the two series, ignoring autodependence, is 0.64.}
  \label{nzd}
\end{figure}

>>>>

<<setup, echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
library(ggplot2)
library(mnormt)
library(tidyr)
library(knitr)
library(nullabor)
library(dplyr)
library(mFilter)
library(grid)
library(gridExtra)
library(stringr)
#library(readr)
#library(lubridate)
# Convert these to read_csv at some point
correl <- read.csv("data/correlations.csv", stringsAsFactors = FALSE) ##Correlations of every plot in every lineup
full <- read.csv("data/full.csv", row.names=1, stringsAsFactors = FALSE) ##MTurk evaluations
prediction <- read.csv("data/predfit.csv") ##fitted data from SAS
time.fit <- read.csv("data/time.csv") ##coefficients for time model from SAS
powercoef <- read.csv("data/PowerEstimates.csv") ##coefficients for power model from SAS

@@

\begin{figure}[htbp]
  \centering
    \begin{subfigure}[htbp]{0.45\textwidth}
    <<nzd, error=FALSE, message=FALSE, warning=FALSE, echo=FALSE>>=
    library(dplyr)
    library(tidyr)
    library(ggplot2)
    rates <- select(read.csv("data/rates.csv"), date, AUD, CNY, NZD)[36:69,]
    rates <- mutate(rates, AUD2=(AUD-mean(AUD))/sd(AUD), CNY2=(CNY-mean(CNY))/sd(CNY)) #scaling
    ggplot(data=rates, aes(x=AUD, y=NZD)) + geom_point()
    @
    \end{subfigure}
    \begin{subfigure}[htbp]{0.45\textwidth}
    <<nzd2, dependson='nzd', error=FALSE, message=FALSE, warning=FALSE, echo=FALSE>>=
    rates_l <- gather(rates, currency, value, -date)
    ggplot(data=subset(rates_l, currency != "CNY" & currency != "CNY2" & currency != "AUD2"), aes(x=as.Date(date), y=value, colour=currency)) + geom_line()
    @
    \end{subfigure}
  \caption{Cross-rates for Australian and NZ dollars against US dollar, from Mar 30-May 2, 2015, shown using a scatterplot (left) and overlaid line graph (right). From which plot is correlation more accurately read? Point-wise correlation between the two series, ignoring autodependence, is 0.64.}
  \label{nzd}
\end{figure}

### 2016-02-01 paper/supplementary.Rnw
Currency rates
Restructure

<<setup, echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
library(maps)
library(ggplot2)
library(dplyr)
library(tidyr)
full <- read.csv("full.csv", row.names=1, stringsAsFactors = FALSE) ##MTurk evaluations
prediction <- read.csv("sas/predfit.csv") ##Large file, very slow, fitted data from SAS
time.fit <- read.csv("sas/time.csv") ##coefficients for time model from SAS
powercoef <- read.csv("sas/PowerEstimates.csv") ##coefficients for power model from SAS

@@

\begin{figure}[htbp]
\centering
<<map, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE, fig.height=3>>=
location <- read.csv("location.csv")
map.dat <- map_data("world")
ggplot() + geom_polygon(aes(long,lat, group=group), fill="grey65", data=map.dat) + theme_bw() +
  geom_point(data=location, aes(x=lon, y=lat, colour= "blue")) +scale_colour_manual(values=c("#FF5500", "#00FFFF")) + theme(aspect.ratio = 0.67, axis.text=element_blank(), axis.title=element_blank(), legend.position="none")
@
\caption{The location of the recruited subjects. The majority reside in North America but some are spread around other countries in Central America, Europe and Asia.}
\label{map}
\end{figure}

\begin{figure}[htbp]
\centering
<<users, dependson='setup', echo=FALSE, results='asis', fig.height=3, message=FALSE, error=FALSE, warning=FALSE>>=
users <- read.csv("turk18_users.csv")
users$academic_study <- factor(users$academic_study)
levels(users$academic_study) <- c("At Most High School", "Some Undergraduate", "Undergraduate Degree", "Some Postgraduate", "Postgraduate Degree")
users$age <- factor(users$age)
levels(users$age) <- c("18-25", "26-30", "31-35", "36-40", "41-45", "46-50", "51-55", "56-60", "61+")
ggplot(data=users, aes(x=age, fill=academic_study)) + geom_bar() + facet_wrap(~gender) +
  scale_fill_manual(name = element_blank(), values=c("#550000", "#883388", "#1133FF", "#FF9933", "#555555")) + labs(x="Age", y=element_blank()) + theme(axis.text.x = element_text(angle = 270))
@
\caption{Age and education by gender. Younger age brackets and males are over-represented in the sample, but these factors caused no significant impact on results.}
\label{ageed}
\end{figure}

>>>>

<<setup, echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
library(maps)
library(ggplot2)
library(dplyr)
library(tidyr)
full <- read.csv("data/full.csv", row.names=1, stringsAsFactors = FALSE) ##MTurk evaluations
prediction <- read.csv("data/predfit.csv") ##Large file, very slow, fitted data from SAS
time.fit <- read.csv("data/time.csv") ##coefficients for time model from SAS
powercoef <- read.csv("data/PowerEstimates.csv") ##coefficients for power model from SAS

@@

\begin{figure}[htbp]
\centering
<<map, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE, fig.height=3>>=
location <- read.csv("data/location.csv")
map.dat <- map_data("world")
ggplot() + geom_polygon(aes(long,lat, group=group), fill="grey65", data=map.dat) + theme_bw() +
  geom_point(data=location, aes(x=lon, y=lat, colour= "blue")) +scale_colour_manual(values=c("#FF5500", "#00FFFF")) + theme(aspect.ratio = 0.67, axis.text=element_blank(), axis.title=element_blank(), legend.position="none")
@
\caption{The location of the recruited subjects. The majority reside in North America but some are spread around other countries in Central America, Europe and Asia.}
\label{map}
\end{figure}

\begin{figure}[htbp]
\centering
<<users, dependson='setup', echo=FALSE, results='asis', fig.height=3, message=FALSE, error=FALSE, warning=FALSE>>=
users <- read.csv("data/turk18_users.csv")
users$academic_study <- factor(users$academic_study)
levels(users$academic_study) <- c("At Most High School", "Some Undergraduate", "Undergraduate Degree", "Some Postgraduate", "Postgraduate Degree")
users$age <- factor(users$age)
levels(users$age) <- c("18-25", "26-30", "31-35", "36-40", "41-45", "46-50", "51-55", "56-60", "61+")
ggplot(data=users, aes(x=age, fill=academic_study)) + geom_bar() + facet_wrap(~gender) +
  scale_fill_manual(name = element_blank(), values=c("#550000", "#883388", "#1133FF", "#FF9933", "#555555")) + labs(x="Age", y=element_blank()) + theme(axis.text.x = element_text(angle = 270))
@
\caption{Age and education by gender. Younger age brackets and males are over-represented in the sample, but these factors caused no significant impact on results.}
\label{ageed}
\end{figure}
